---
title: "Lab 5 Salamanders"
author: "Joshua Driscoll"
date: "10/13/2021"
output: html_document
---
* Environmental Code
```{r}
library(here)
ricker_fun = function(x, a, b) 
{
  return(a * x * exp(-b * x))
}

line_point_slope = function(x, x1, y1, slope)
  {
    get_y_intercept = 
      function(x1, y1, slope) 
        return(-(x1 * slope) + y1)
    
    linear = 
      function(x, yint, slope) 
        return(yint + x * slope)
    
    return(linear(x, get_y_intercept(x1, y1, slope), slope))
}

dispersal <- read.csv(here("data", "dispersal.csv"))

```

* Q1

```{r}
exp_fun = function(x, a, b)
{return(a*exp(-b * x))}
```

* Q2
```{r}
curve(exp_fun(x, 1.9, .1), add = FALSE, from = 0, to = 50,
 ann = FALSE, axes = TRUE, ylab = "f(x)"); box()
curve(exp_fun(x, 1.9, .3), lty = "dotted", add = TRUE)
curve(exp_fun(x, 1.2, .2), col = "red", add = TRUE)
curve(exp_fun(x, 1.2, .4), col = "red", lty = "dotted", add = TRUE)
title(main = "Exponential Curves", ylab = "f(x)")

```

** **For some reason the title wouldn't display when the main argument was within the first curve function so I improvised with title**

* Q3

When you change the a parameter, the graph has a lower y intercept and the position of the graph changes. When changing the a parameter by -.7 in this example, the graph shifts down the y axis. The a parameter alters the y intercept.

* Q4

When you change the b parameter, the slope of the graph changes. When changing the b parameter in this example, the slope gets steeper with higher values of b.

* Q5
```{r}
curve(
  ricker_fun(x, 25, .1), add = FALSE, from = 0, to = 75, 
  main = "Ricker functions",
  ylab = "f(x)", xlab = "x")
curve(
  ricker_fun(x, 20, .2), lty = "dotted", add = TRUE)
curve(
  ricker_fun(x, 10, .2), lty = "dotted", add = TRUE)
curve(
  ricker_fun(x, 75, .3), col = "red", add = TRUE)
curve(
  ricker_fun(x, 50, .3), col = "red", lty = "dotted", add = TRUE)
curve(
  ricker_fun(x, 40, .3), col = "red", lty = "dotted", add = TRUE)
```

* Q6

As you change the a parameter the initial slope of the graph changes. This causes the graph to get taller as the slope of the initial line increases.

* Q7

As you change the b parameter the height of the graph changes. This causes the graph to get shorter or taller depending on the value of b that is input.

* Q8

Slope: -.0004

X: 503

Y: .4

I chose the X and Y parameters by looking for a centralized point using the Locator(1) function. Once I had the X and Y of my point, I used trial and error to find the slope. I originally had dificulty as my slope was nowhere near small enough to look correct but then I looked at the scale of the X axis and figured it out. 

* Q 9
```{r}
plot(x = dispersal$dist.class, y = dispersal$disp.rate.ftb, main = "Salamander Dispersal", xlab = "Dispersal Class", ylab = "1st Breeding Season Dispersal Rate")
curve(line_point_slope(x, 503, .4, -.0004), add = TRUE)
```

* Q 10

a = 1.2

b = .003

To choose these parameters I had to ask another student (Sonja) for assistance. After discussion and some trial and error, we decided that a should be a number close to the numbers represented on the X axis as this number represents where the curve is going to begin. Then we chose a shallow slope again due to the scale of the X axis.

* Q 11
```{r}
plot(x = dispersal$dist.class, y = dispersal$disp.rate.ftb, main = "Salamander Dispersal", xlab = "Dispersal Class", ylab = "1st Breeding Season Dispersal Rate")
curve(exp_fun(x, 1.2, .003), add = TRUE)
```

* Q 12

a = .009

b = .004

I found these values by starting with my values for the exponential function and then using a lot of trial and error to find the correct values. While I understand what a and b change in the equation, it was difficult to translate that knowledge into a good guess for a and b in a real world scenario.

* Q 13
```{r}
plot(x = dispersal$dist.class, y = dispersal$disp.rate.ftb, main = "Salamander Dispersal", xlab = "Dispersal Class", ylab = "1st Breeding Season Dispersal Rate")
curve(ricker_fun(x, .009, .004), add = TRUE)
```

* Q 14

```{r}
linear_pred <- line_point_slope(dispersal$dist.class, 503, .4, -.0004)
resids_linear <- (dispersal$disp.rate.ftb) - linear_pred

exp_pred <- exp_fun(dispersal$dist.class, 1.2, .003)
resids_exp <- (dispersal$disp.rate.ftb) - exp_pred

rick_pred <- ricker_fun(dispersal$dist.class, .009, .004)
resids_ricker <- (dispersal$disp.rate.ftb) - rick_pred

data.frame(resids_linear, resids_exp, resids_ricker)

```

* Q 15
```{r}
par(mfrow = c(3, 1))
hist(resids_linear, main = "Linear Residuals", xlab = "Residuals")
hist(resids_exp, main = "Exponential Residuals", xlab = "Residuals")
hist(resids_ricker, main = "Ricker Residuals", xlab = "Residuals")
```


