---
title: "LAB_7"
author: "Joshua Driscoll"
date: "10/31/2021"
output: html_document
---

* Loading Penguins and installing packages

```{r}
library(palmerpenguins)
```

* Q 1

The sample size is 123.

```{r}

gentoo <- subset(penguins, species == "Gentoo", select = c(species, bill_length_mm))

g = na.omit(gentoo$bill_length_mm)
length(g)

```


* Q 2

The sample standard deviation is 3.081857.

```{r}

sd(g, na.rm = TRUE)

```

* Q 3

The critical T value is 1.657439.

```{r}

qt(.95, df = 122, lower.tail = TRUE)

```

* Q 4

The sample standard error is 0.2778817.

```{r}

sse_mean = function(x)
{
  y = na.omit(x)
  return((sd(y))/sqrt(length(y)))
}

sse_mean(g)

```

* Q 5

The CI radius is .4605721. The mean of the dataset is 47.40488. Given that the CI is expressed as the mean +/- the CI radius, the CI is 47.40488 +/- .4605721.

```{r}

# Multiplying SSE by critical T value for CI radius

a = qt(.95, df = 122, lower.tail = TRUE)
b = sse_mean(g)

a * b

# Finding mean of dataset

mean(g)

```

* Q 6

The CI is 47.50488 +/- 0.4607168.

* Q 7

```{r}

require(boot)

boot_mean = function(x, i)
{
  return(mean(x[i], na.rm = TRUE))
}

myboot = boot(data = g, statistic = boot_mean, R = 10000)
print(myboot)

```

* Q 8

```{r}

quantile(
  myboot$t,
  c(0.025, 0.975))

```


* Q 9

```{r}

rarefaction_sampler = function(input_dat, n_iterations)
{
    n_input_rows = nrow(input_dat)
    
    results_out = matrix(
        nrow = n_iterations,
        ncol = n_input_rows)
    
    for(i in 1:n_iterations)
    {
    
        for(j in 1:n_input_rows)
        {
            
            rows_j = sample(n_input_rows, size = j, replace=TRUE)
            
            t1 = input_dat[rows_j, ]
            
            t2 = apply(t1, 2, sum)
            
            results_out[i, j] = sum(t2 > 0)
        }
    }
    return(results_out)
}


```

* Q 10

I still don't quite understand the for loops. I understand what they do to the point where I could follow along and create one but I still am lacking a fundamental understanding of the loop variable and how that playing into why and how the function is looping through the code.

* Q 11

```{r}
library(here)

moths = read.csv(here("data", "moths.csv"))
rarefact = rarefaction_sampler(moths[,-1], 10000)

rare_mean = apply(rarefact, 2, mean)
rare_quant = apply(rarefact, 2, quantile, probs=c(0.025, 0.975))
rare = t(rbind(rare_mean, rare_quant))

```

* Q 12

```{r}

print(matplot(
  rare,
  type='l',
  lwd = 2,
  col = "red",
  xlab='Number of sampling plots',
  ylab='Species richness',
  main='Moth Rarefaction Curve'))

legend(
  'bottomright',
  legend=c('Average Species Seen','Upper Confidence Envelope (2.5%)','Lower Confidence Envelope (97.5%)'),
  lty=c(1,2,3),col=c(1,2,3), inset=c(.1,.1))

```

* Q 13

If we round up and say that any value past 9.5 species correlates to seeing all 10, then looking at the rarefaction curve I see that to see 9.5 species I have to go to at least 10 sites.

